Tail Flexibility in the Degrees of Preferential

### 2025-04-30 paper.qmd
mv *rds results/; edit *R accordingly; pdf still reproduced

surfit_list = list()
pars = readRDS('recovery_pars.rds')
recovery_list = readRDS('recovery_dat.rds')
selected = c(1,27,14,35)
# selected = 1:36
for(k in 1:length(selected)){
  j=selected[k]
  x = recovery_list[[j]]$mcmc$dat[,1]
  ls = c()

@@

plt1 = readRDS('comp_plot.rds')

@@

plt2 = readRDS('shape_plot.rds')

@@

plt3 = readRDS('PA_plot.rds')
plot(plt3)

>>>>

surfit_list = list()
pars = readRDS('results/recovery_pars.rds')
recovery_list = readRDS('results/recovery_dat.rds')
selected = c(1,27,14,35)
# selected = 1:36
for(k in 1:length(selected)){
  j=selected[k]
  x = recovery_list[[j]]$mcmc$dat[,1]
  ls = c()

@@

plt1 = readRDS('results/comp_plot.rds')

@@

plt2 = readRDS('results/shape_plot.rds')

@@

plt3 = readRDS('results/PA_plot.rds')
plot(plt3)
